Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex

To delve one step deeper in our analysis, parallel communications are usually expressed by architecture parameters---$\alpha$, $\beta$ and $\gamma$

@@

The Parareal method TODO does this scale well?

>>>>

To delve one step deeper in our analysis, parallel communications are usually expressed by architecture parameters - $\alpha$, $\beta$ and $gamma$ explained in the below table.

\begin{table}
\centering
\begin{tabular}{|c|l|}
{\bf Variable} & {\bf Description}\\
\hline\hline
$\alpha$ & Latency of communication. (sec)\\
$\beta$ & Inverse communication bandwidth. (sec/byte)\\
$\gamma$ & Inverse computational performance. (sec/flop)\\
\hline
\end{tabular}
\caption{Table of Communication Architecture Parameters}
\label{tab:notation}
\end{table}

\subsubsection{Parareal}
TODO THIS IS CONFUSING Wesley

\subsubsection{Parallel By Space}
TODO THIS IS CONFUSING TOO Wesley

@@

We first try to express $B$ as function of the quality factor $Q$ and the number of correction steps of the parareal $k$.

From our analysis in equation~\ref{eq:scheme}, when we set $N$ to 1 for the generic setup, we see that our total computation is $t + K(t+ Qt)$.  Of this, the only parallelizable part is the $kQt$ term.  Thus to find the expression of the parallelizable portion, we simplify:

\[
AA
\]

Now to replace this into Amdahl's Law, we have:
